---
title: "HW01_gapminder"
output: md_document
---
##Loading Data Frame into R markdown
In order to work with Data Frames, we load the gapminder using the command library()
```{r}
library(gapminder)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Overview of the Data set
The command summary() gives a statistical overview of what the data frame looks like
```{r}
summary(gapminder)
```

##Data exploration
The following set of commands gives a brief information about the data set
```{r}

str(gapminder)
head(gapminder)
tail(gapminder)
```

```{r}
class(gapminder)
```

```{r}
names(gapminder)
```
```{r}
ncol(gapminder)
nrow(gapminder)
length(gapminder)
```

##Plotting and Data Visualisation
Plots are used to properly visualise the data set and R code chunks could be used for plotting
```{r}
plot(lifeExp~log(pop), gapminder)
plot(lifeExp~log(log(gdpPercap)), gapminder)
```

##Working with a single variable of the data set
$ sign is used to specify a single variable in the data set. the following set of commands explores each set of the gapminder data frame
```{r}
class(gapminder$country)
levels(gapminder$country)
```

```{r}
summary(gapminder$continent)
nlevels(gapminder$continent)
table(gapminder$continent)
```
```{r}
summary(gapminder$lifeExp)
hist(gapminder$lifeExp)
barplot(table(gapminder$continent))
```

